Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-11-04 ms.tex
summarized the various sources of noise that we discussed in our asic dewar meeting 2018-11-02

Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
The resets cause discontinuities in the pedestal level of all pixels between frames. This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can. These are discussed in Section \ref{sec:preAmp}.
	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
	\item \textbf{Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the detectors. For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}. Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to $\lesssim$ 1 mK.
\end{itemize}

>>>>

Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
The resets cause discontinuities in the pedestal level of all pixels between frames. This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can. These are discussed in Section \ref{sec:preAmp}.
	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the detectors. For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}. Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to $\lesssim$ 1 mK.
	\item \textbf{ASIC Temperature Fluctuations:} The asic temperature will change as the operating mode. For example, in the CV3 stability test, the temperature of the A asic changed by $\sim$80 mK when the readout mode was switched from full frame to subarray. This temperature change is expected to be smaller in flight due to adjustments in ?? (Marcia said in 2018-11-02 meeting)
	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination. Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array.
	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Add more details and citations}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers. If the detector fringe pattern changes with time, it will change the throughput of a grism image.
\end{itemize}

It should be noted that the detector effects related to the asic circuit can be specific to the ``personality'' of each asic. The asics all have different asic load files which are tuned to minimize the power consumption and dark current in a particular asic. Since the asic load files are specific to each detector, they may exhibit different noise properties.
